\section{Conclusion}
We have successfully developed the Application ‘DOGSTORE’ With the help of various links and tools, we have been able to provide a moblie application which is live and running successfully. This project also provide the values and ethics of how to deal with the real customer. We have been successful in our attempt to take care of the needs of both the visitors as well as the administrator. Finally we hope that this will go a long way in popularizing the organization. The system has reached a steady state where all the bugs have been eliminated. The website is developed at a high level of efficiency and all the visitors associated with the application understand its advantage. The system solves the problem it was intended to solve as requirement specification.

 
\section{Future Scope}
The app uses android technology which has evergreen scope. The app obviously
has a bright future scope as there is test which includes different level and type of
questions. Moreover in Future, one can see his/her earlier records regarding the
payments and can checkout the product with the use of image processing, by simply placing the camera on previous buyed product. The platform used is android. Nowadays Android has
become very popular which is an open-source, Linux-based operating system
mainly designed by Google for smart-phones and tablets.

Many mobile Apps development industries are considering Android Application
Development as one of the best business opportunities, for this they need to
hire a lot of knowledgeable mobile application developer in future. This adds a
big sign of scope of mobile Apps in future.

In the current job market of mobile application development, the need for inventive
App developers is huge and still increasing. Android Apps development can also
be taken up as a part time job. You can create your own applications at home and
submit it to the Google Play store which can be downloaded by smart-phone users.