\section{Introduction to Organization}

Forget about not remembering where you spent your money! Keep track of your expenses and get
a lot of statistics to know in what you spend more and you can evaluate where you can cut some expenses! Take advantage of this tool that will help you to manage your money and be informed
all the time. You can also configure to get notifications when you have to make some payments
every month so you dont forget! This Application is made for any user who wants or wish to keep a better track of their expenses in order to keep them in a same place.
\section{Introduction To Project} 
With the launch and increase in sales of smartphones over the last few years, people are using mobile applications to get their work done, which makes their lives easier. Mobile applications comprise various different categories such as Entertainment, Sports, Lifestyle, Education, Games, Food and Drink, Health and Fitness, Finance, etc. This Expense Tracker application falls in the Finance Category and serves the important purpose of managing finances which is a very important part of one’s life.  The software product went through the design, development, and the testing phase as a part of the Software Development Lifecycle. 

The application’s interface is designed using custom art elements, the functionality is implemented using Android SDK, and the phase of testing the product was accomplished successfully. The application is not much user intensive but just comprises of having them enter the expense amount, date, category, merchant and other optional attributes (taking picture of the receipts, entering notes about the expense, adding subcategories to the categories). With this entered information, the user is able to see the expense details about the product,price,quality,quantity or category. All these topics have been explained in detail in their respective chapters

\section{Project Category}
Our Project is internet based.
Dog lovers can get products,vaxines,chains calcium tablets, bones of their choice.They can get stuff deliver to their homes. This application helps them to find needy products for their pet dogs. They can search products according to need of their pet dogs.


\section{Objectives}

\begin{itemize}
	\item The objective of our project is to provide information to dog lovers about ideal and best products for their pet dogs.
	\item We want to facilitate by providing them description about different products and their quality. 
	\item One of the biggest objective is to aware the doglovers about different products of different quality so they  can choose the right product.
	\item Implement the various concepts of Android programming together within an application that becomes helpful for intended users.
	\item Developing an Android based application for the dog lovers and system having user friendly interface.
	\item Read on for help with choosing a dog's food, training, first aid and vet visits, walks, dog sitters, GPS trackers.
	\item To make life better. Even better is when they combine to make everything easier, because dog lovers don't need to go to market for dog's food,chains,calcium bones,vaxines.they get these all stuff online.
\end{itemize}
 

\section{Problem Formulation}
A Problem well defined is a problem half solved.Formulating a Problem Formulation is the first and most important step of a research process. It fits the level of researcher’s level of research skills, needed resources and time restrictions and can be investigated through the collection and analysis of data 
Our team will give proper attention to the visitor problems.   
We are also providing contact system in our project  ,if any visitor find something wrong in our content then  they can contact us . 
We will welcome any type of suggestion and if we find it right then we will implement that suggestion in our application.


\section{Identification/Reorganization of Need}
Our Dogstore basically targets different segments to fulfill the desired needs of people which are following below:-
\begin{itemize}
\item The needs of our project is to ignite the interest in care and love about their pet dogs.
\item We want to facilitate people by providing them different forms of products and quality.
\item For the enquries customers also interact to the artificial intelligence system.
\end{itemize}

\section{Existing System}
In the existing system , we have some applications on the internet in which there is least information about products and feed of pet dogs but we are providing that facility too. Some applications does not have pay online facility.We did not find any application on the internet which provide detailed information about different products collectively but we have tried to give facilities like AI system,payment by payU.So,all in all our site is user friendly site.   

\section{Proposed System}
To remove the limitations of the existing system , In the proposed system , people can easily get information about all the products of pet dogs. We are providing online ordering in our project so that people can have reach to our facilities easily.

\section{Unique Features of the System}
\subsection{Complete Application Built Instantly}
As soon as you join our application is created for you. Every page has text and photos to help you get started.  
\subsection{Collective Information}
We did not find any application on the internet which provide detailed information about different products collectively but we have tried to give facilities like AI system,payment by payU. 
\subsection{User Friendly}
Our application is very user friendly .Design is simple and effective. People can reach to different section easily.




